---
title: "GEOM WHIM Descriptor MAE QC"
author: "Michael Tran"
date: "`r format(Sys.Date(), '%Y-%m-%d')`"
output:
  html_document:
    toc: true
    toc_float: true
    toc_depth: 3
    code_folding: show
---

This notebook demonstrates the structure and basic use of the final
`MultiAssayExperiment` containing GEOM-derived WHIM descriptor assays and
compound annotations.

WHIM, or Weighted Holistic Invariant Molecular, descriptors summarize 3D 
molecular shape from conformer coordinates. In the pipeline, RDKit computes 
WHIM descriptors for GEOM conformers with valid Boltzmann weights, and the assay 
matrices store three compound-level summaries: the highest-probability 
conformer (`WHIM_hp`), the arithmetic mean across valid conformers (`WHIM_avg`), 
and the Boltzmann-weighted mean across valid conformers (`WHIM_wavg`).

WHIM descriptors were introduced by Todeschini, Gramatica, Provenzani, and
Marengo in *Chemometrics and Intelligent Laboratory Systems*:
<https://doi.org/10.1016/0169-7439(95)80026-6>.

## Setup

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo = TRUE,
  message = FALSE,
  warning = FALSE,
  fig.width = 8,
  fig.height = 5
)

suppressPackageStartupMessages({
  library(MultiAssayExperiment)
  library(SummarizedExperiment)
  library(S4Vectors)
  library(dplyr)
  library(tidyr)
  library(tibble)
  library(ggplot2)
  library(knitr)
  library(scales)
  library(uwot)
})

theme_set(theme_minimal(base_size = 12))

project_root <- normalizePath(
  if (dir.exists("data/results")) "." else "..",
  winslash = "/",
  mustWork = TRUE
)
knitr::opts_knit$set(root.dir = project_root)

mae_path <- file.path(
  project_root,
  "data",
  "results",
  "geom_MultiAssayExperiment.rds"
)

if (!file.exists(mae_path)) {
  stop("MAE file not found: ", mae_path)
}

fmt_count <- function(x) {
  format(x, big.mark = ",", scientific = FALSE, trim = TRUE)
}

fmt_number <- function(x, digits = 2) {
  format(round(x, digits), big.mark = ",", scientific = FALSE, trim = TRUE)
}

fmt_percent <- function(x, digits = 1) {
  paste0(format(round(100 * x, digits), nsmall = digits, trim = TRUE), "%")
}

is_present <- function(x) {
  !is.na(x) & nzchar(trimws(as.character(x)))
}

sample_values <- function(matrix, n = 200000L) {
  values <- as.vector(matrix)
  values <- values[is.finite(values)]
  if (length(values) > n) {
    set.seed(20260430)
    values <- sample(values, n)
  }
  values
}
```

## Load the MAE

```{r load-data}
mae <- readRDS(mae_path)

assay_names <- names(experiments(mae))
assay_mats <- setNames(
  lapply(assay_names, \(assay_name) assay(experiments(mae)[[assay_name]])),
  assay_names
)

compound_metadata <- as.data.frame(metadata(mae)$Drug.Metadata) |>
  rownames_to_column("Compound.Key") |>
  as_tibble()

coldata <- as.data.frame(colData(mae)) |>
  as_tibble()

rowdata <- bind_rows(
  lapply(assay_names, \(assay_name) {
    as.data.frame(rowData(experiments(mae)[[assay_name]])) |>
      as_tibble() |>
      mutate(Assay = assay_name)
  })
)

mae
```

## Dataset Overview

```{r dataset-overview, class.source="fold-hide"}
assay_summary <- tibble(
  assay = assay_names,
  assay_name = vapply(
    assay_names,
    \(assay_name) {
      paste(assayNames(experiments(mae)[[assay_name]]), collapse = ", ")
    },
    character(1)
  ),
  features = vapply(
    assay_names,
    \(assay_name) nrow(assay_mats[[assay_name]]),
    integer(1)
  ),
  compounds = vapply(
    assay_names,
    \(assay_name) ncol(assay_mats[[assay_name]]),
    integer(1)
  ),
  feature_type = "WHIM descriptor features"
)

annotation_availability <- compound_metadata |>
  mutate(
    annotation_status = if_else(
      In.AnnotationDB,
      "AnnotationDB enriched",
      "No AnnotationDB match",
      missing = "No AnnotationDB match"
    )
  ) |>
  count(annotation_status, name = "compounds") |>
  mutate(
    fraction = compounds / sum(compounds),
    percent = scales::percent(fraction, accuracy = 0.1),
    label = paste0(
      annotation_status,
      "\n",
      scales::comma(compounds),
      " (",
      percent,
      ")"
    )
  )

overview_tbl <- tibble(
  quantity = c(
    "Pipeline ID",
    "Pipeline version",
    "Experiments",
    "Assays",
    "Compounds in colData",
    "Drug metadata records",
    "Source subsets",
    "WHIM features per assay",
    "Total assay columns",
    "Compounds with PubChem CID",
    "Compounds without PubChem CID",
    "Median total conformers",
    "Median unique conformers"
  ),
  value = c(
    metadata(mae)$Pipeline$ID,
    metadata(mae)$Pipeline$Version,
    fmt_count(length(experiments(mae))),
    paste(assay_names, collapse = ", "),
    fmt_count(nrow(coldata)),
    fmt_count(nrow(compound_metadata)),
    paste(sort(unique(compound_metadata$GEOM.Source.Subset)), collapse = ", "),
    fmt_count(unique(assay_summary$features)),
    fmt_count(sum(assay_summary$compounds)),
    fmt_count(sum(!is.na(compound_metadata$Pubchem.CID))),
    fmt_count(sum(is.na(compound_metadata$Pubchem.CID))),
    fmt_count(stats::median(
      compound_metadata$GEOM.Total.Conformers,
      na.rm = TRUE
    )),
    fmt_count(stats::median(
      compound_metadata$GEOM.Unique.Conformers,
      na.rm = TRUE
    ))
  )
)

kable(overview_tbl)
```

```{r assay-summary}
kable(assay_summary)
```

This MAE contains three WHIM descriptor assays. Rows are descriptor features and
columns are compounds keyed by `GEOM.Source.SMILES`. The object is
compound-level: each assay column represents one GEOM drug compound.

## Inspect the MAE Structure

The object layout is inspected directly below. The experiment container, assay
names, compound-level metadata, sample map, and object-level metadata can all be
accessed from the printed structure and the code shown in this section.

```{r object-contents}
mae

experiments(mae)

colnames(colData(mae))

head(as.data.frame(sampleMap(mae)))

names(metadata(mae))
```

The `sampleMap` has one row for each assay-compound pair. For every assay, both
`primary` and `colname` are `GEOM.Source.SMILES`, so the same compound metadata
row maps to that compound's column in each WHIM assay.

## Compound Metadata

```{r compound-metadata-head}
compound_metadata |>
  select(
    GEOM.Source.SMILES,
    Pubchem.CID,
    InChIKey,
    In.AnnotationDB,
    AnnotationDB.Name,
    GEOM.Source.Subset,
    GEOM.Charge,
    GEOM.Total.Conformers,
    GEOM.Unique.Conformers,
    GEOM.Lowest.Energy,
    GEOM.Ensemble.Energy
  ) |>
  slice_head(n = 8) |>
  kable()
```

The main fields commonly used in downstream analysis are:

* `GEOM.Source.SMILES`: the GEOM source molecule key used as the MAE primary key and assay column name.
* `Pubchem.CID`: the PubChem compound identifier used to join back to the base harmonized drug dataset.
* `InChIKey`: the structure-level identifier derived from the representative GEOM conformer molecule.
* `GEOM.RDKit.SMILES` and `GEOM.Canonical.SMILES`: RDKit-derived structures retained for comparison with the source key.
* `In.AnnotationDB`: whether the compound mapped to AnnotationDB metadata.
* `GEOM.Total.Conformers` and `GEOM.Unique.Conformers`: GEOM conformer counts carried into the compound-level metadata.
* `GEOM.Lowest.Energy` and `GEOM.Ensemble.Energy`: GEOM energy summaries for the compound.

```{r metadata-completeness}
metadata_completeness <- compound_metadata |>
  summarise(
    across(
      c(
        Pubchem.CID,
        InChIKey,
        GEOM.RDKit.SMILES,
        GEOM.Canonical.SMILES,
        AnnotationDB.Name,
        AnnotationDB.SMILES,
        GEOM.Charge,
        GEOM.Total.Conformers,
        GEOM.Unique.Conformers,
        GEOM.Lowest.Energy,
        GEOM.Ensemble.Energy
      ),
      \(value) sum(is_present(value))
    )
  ) |>
  pivot_longer(
    cols = everything(),
    names_to = "field",
    values_to = "present"
  ) |>
  mutate(
    missing = nrow(compound_metadata) - present,
    percent_present = fmt_percent(present / nrow(compound_metadata))
  ) |>
  arrange(desc(present))

kable(metadata_completeness)
```

```{r annotationdb-coverage, fig.height=4.5, fig.width=7}
kable(
  annotation_availability |>
    select(annotation_status, compounds, percent)
)

ggplot(
  annotation_availability,
  aes(x = "", y = fraction, fill = annotation_status)
) +
  geom_col(width = 1, color = "white") +
  geom_text(
    aes(label = label),
    position = position_stack(vjust = 0.5),
    lineheight = 0.95
  ) +
  coord_polar(theta = "y") +
  scale_fill_manual(values = c("#4C956C", "#C75C5C")) +
  labs(
    title = "AnnotationDB metadata availability for GEOM compounds",
    fill = NULL
  ) +
  theme_void()
```

## Conformer Landscape

GEOM provides conformer-level structure summaries. The MAE stores compound-level
conformer counts and energy summaries in `colData`.

```{r conformer-count-summary}
conformer_summary_tbl <- compound_metadata |>
  summarise(
    compounds = n(),
    total_conformer_min = min(GEOM.Total.Conformers, na.rm = TRUE),
    total_conformer_median = stats::median(GEOM.Total.Conformers, na.rm = TRUE),
    total_conformer_mean = mean(GEOM.Total.Conformers, na.rm = TRUE),
    total_conformer_max = max(GEOM.Total.Conformers, na.rm = TRUE),
    unique_conformer_min = min(GEOM.Unique.Conformers, na.rm = TRUE),
    unique_conformer_median = stats::median(
      GEOM.Unique.Conformers,
      na.rm = TRUE
    ),
    unique_conformer_mean = mean(GEOM.Unique.Conformers, na.rm = TRUE),
    unique_conformer_max = max(GEOM.Unique.Conformers, na.rm = TRUE)
  ) |>
  mutate(across(everything(), fmt_number))

kable(conformer_summary_tbl)
```

```{r conformer-count-histogram, fig.height=4.5}
compound_metadata |>
  transmute(
    `Total conformers` = pmax(GEOM.Total.Conformers, 1),
    `Unique conformers` = pmax(GEOM.Unique.Conformers, 1)
  ) |>
  pivot_longer(
    cols = everything(),
    names_to = "count_type",
    values_to = "conformers"
  ) |>
  ggplot(aes(x = conformers, fill = count_type)) +
  geom_histogram(bins = 50, alpha = 0.7, position = "identity") +
  scale_x_log10(labels = scales::comma) +
  scale_fill_manual(values = c("#8EA8C3", "#D49A3A")) +
  labs(
    title = "GEOM conformer count distribution",
    x = "Conformers per compound",
    y = "Number of compounds",
    fill = NULL
  )
```

```{r lowest-energy-plot, fig.height=4}
compound_metadata |>
  filter(is.finite(GEOM.Lowest.Energy)) |>
  ggplot(aes(x = GEOM.Lowest.Energy)) +
  geom_histogram(bins = 70, fill = "#3B6EA8", color = "white") +
  labs(
    title = "GEOM lowest conformer energy",
    x = "Lowest energy",
    y = "Number of compounds"
  )
```

```{r ensemble-energy-plot, fig.height=4}
compound_metadata |>
  filter(is.finite(GEOM.Ensemble.Energy)) |>
  ggplot(aes(x = GEOM.Ensemble.Energy)) +
  geom_histogram(bins = 70, fill = "#6E9F64", color = "white") +
  labs(
    title = "GEOM ensemble energy",
    x = "Ensemble energy",
    y = "Number of compounds"
  )
```

```{r charge-distribution, fig.height=4.5}
compound_metadata |>
  count(GEOM.Charge, name = "compounds") |>
  ggplot(aes(x = factor(GEOM.Charge), y = compounds)) +
  geom_col(fill = "#7D5BA6") +
  scale_y_log10(labels = scales::comma) +
  labs(
    title = "Compound charge distribution",
    x = "GEOM charge",
    y = "Number of compounds"
  )
```

```{r highest-conformer-counts}
compound_metadata |>
  arrange(desc(GEOM.Total.Conformers), GEOM.Source.SMILES) |>
  select(
    GEOM.Source.SMILES,
    Pubchem.CID,
    In.AnnotationDB,
    GEOM.Total.Conformers,
    GEOM.Unique.Conformers,
    GEOM.Lowest.Energy,
    GEOM.Ensemble.Energy
  ) |>
  slice_head(n = 12) |>
  kable()
```

## WHIM Descriptor Assays

```{r rowdata-head}
rowdata |>
  select(Assay, Feature.ID, Feature.Index, Assay.Name) |>
  filter(Assay == "WHIM_hp") |>
  slice_head(n = 6) |>
  kable()
```

```{r assay-quality-summary}
assay_quality_tbl <- bind_rows(
  lapply(assay_names, \(assay_name) {
    mat <- assay_mats[[assay_name]]
    sampled_values <- sample_values(mat)
    tibble(
      assay = assay_name,
      features = nrow(mat),
      compounds = ncol(mat),
      entries = length(mat),
      missing_entries = sum(is.na(mat)),
      non_finite_entries = sum(!is.finite(mat)),
      sampled_min = min(sampled_values, na.rm = TRUE),
      sampled_median = stats::median(sampled_values, na.rm = TRUE),
      sampled_mean = mean(sampled_values, na.rm = TRUE),
      sampled_max = max(sampled_values, na.rm = TRUE)
    )
  })
) |>
  mutate(
    across(
      c(features, compounds, entries, missing_entries, non_finite_entries),
      fmt_count
    ),
    across(
      c(sampled_min, sampled_median, sampled_mean, sampled_max),
      \(value) fmt_number(value, 4)
    )
  )

kable(assay_quality_tbl)
```

```{r feature-variability, include=FALSE}
feature_stats <- bind_rows(
  lapply(assay_names, \(assay_name) {
    mat <- assay_mats[[assay_name]]
    tibble(
      Assay = assay_name,
      Feature.ID = rownames(mat),
      Mean = rowMeans(mat, na.rm = TRUE),
      SD = apply(mat, 1, stats::sd, na.rm = TRUE)
    )
  })
) |>
  left_join(rowdata, by = c("Assay", "Feature.ID")) |>
  arrange(Assay, desc(SD))
```

```{r feature-variability-plot, fig.height=7, fig.width=9}
feature_stats |>
  group_by(Assay) |>
  slice_max(SD, n = 12, with_ties = FALSE) |>
  ungroup() |>
  mutate(
    Feature.Label = reorder(Feature.ID, SD)
  ) |>
  ggplot(aes(x = SD, y = Feature.Label, fill = Assay)) +
  geom_col(show.legend = FALSE) +
  facet_wrap(~Assay, scales = "free_y") +
  labs(
    title = "Most variable WHIM descriptor features",
    x = "Standard deviation across compounds",
    y = "Feature"
  )
```

## Descriptor-Space UMAP

The UMAP below is a visualization of a reproducible sample of compounds using
all three WHIM assay families. Each point is one compound-level descriptor
profile.

```{r descriptor-umap, fig.height=5.5, fig.width=7}
set.seed(20260430)

umap_compound_source <- compound_metadata |>
  filter(GEOM.Source.SMILES %in% colnames(assay_mats[[assay_names[[1L]]]]))

umap_sample_n <- min(3000L, nrow(umap_compound_source))

umap_compounds <- umap_compound_source |>
  slice_sample(n = umap_sample_n)

umap_input <- do.call(
  cbind,
  lapply(assay_names, \(assay_name) {
    mat <- assay_mats[[assay_name]][,
      umap_compounds$GEOM.Source.SMILES,
      drop = FALSE
    ]
    t(mat)
  })
)

umap_input <- scale(umap_input)
umap_input[is.na(umap_input)] <- 0

umap_layout <- uwot::umap(
  umap_input,
  n_neighbors = 15,
  min_dist = 0.2,
  metric = "cosine",
  n_threads = 1,
  n_sgd_threads = 1,
  verbose = FALSE
)

umap_tbl <- as_tibble(umap_layout, .name_repair = \(x) c("UMAP1", "UMAP2")) |>
  bind_cols(
    umap_compounds |>
      select(
        GEOM.Source.SMILES,
        GEOM.Unique.Conformers,
        GEOM.Total.Conformers
      )
  ) |>
  mutate(Unique.Conformers.For.Color = pmax(GEOM.Unique.Conformers, 1))

ggplot(
  umap_tbl,
  aes(
    x = UMAP1,
    y = UMAP2,
    color = Unique.Conformers.For.Color
  )
) +
  geom_point(alpha = 0.75, size = 1.2) +
  scale_color_gradient(
    low = "#D8E7F1",
    high = "#1F5F8B",
    trans = "log10",
    labels = scales::comma
  ) +
  labs(
    title = "UMAP of sampled GEOM WHIM descriptor profiles",
    subtitle = paste0(
      "Compound-level descriptors for ",
      scales::comma(nrow(umap_tbl)),
      " sampled compounds."
    ),
    x = "UMAP 1",
    y = "UMAP 2",
    color = "Unique\nconformers"
  )
```

## Assay Relationship Checks

The three WHIM assays use the same compounds and feature count, but summarize
conformer information differently. The plot below compares normalized
per-compound descriptor-vector distances between assay pairs.

```{r assay-pair-distances, fig.height=5.5, fig.width=9}
assay_pairs <- tribble(
  ~pair                     , ~assay_a    , ~assay_b     , ~denominator_assay ,
  "WHIM_hp vs WHIMS_avg"    , "WHIM_hp"   , "WHIMS_avg"  , "WHIMS_avg"        ,
  "WHIM_hp vs WHIMS_wavg"   , "WHIM_hp"   , "WHIMS_wavg" , "WHIMS_wavg"       ,
  "WHIMS_avg vs WHIMS_wavg" , "WHIMS_avg" , "WHIMS_wavg" , "WHIMS_avg"
)

assay_distance_tbl <- bind_rows(
  lapply(seq_len(nrow(assay_pairs)), \(index) {
    difference <- assay_mats[[assay_pairs$assay_a[[index]]]] -
      assay_mats[[assay_pairs$assay_b[[index]]]]
    absolute_distance <- sqrt(colSums(difference * difference, na.rm = TRUE))
    denominator_norm <- sqrt(
      colSums(
        assay_mats[[assay_pairs$denominator_assay[[index]]]]^2,
        na.rm = TRUE
      )
    )

    tibble(
      pair = assay_pairs$pair[[index]],
      normalized_distance = absolute_distance /
        pmax(
          denominator_norm,
          .Machine$double.eps
        )
    )
  })
)

assay_distance_tbl |>
  filter(normalized_distance > 0) |>
  ggplot(aes(x = normalized_distance, fill = pair)) +
  geom_histogram(bins = 80, color = "white", show.legend = FALSE) +
  facet_wrap(~pair, scales = "free_y") +
  scale_y_log10(labels = scales::comma) +
  labs(
    title = "Normalized pairwise distances between WHIM assay summaries",
    subtitle = "Exact-zero distances are omitted to show the non-zero spread.",
    x = "Normalized descriptor-vector distance",
    y = "Number of compounds"
  )
```

## High-Variance Descriptor Snapshot

This heatmap shows the most variable descriptor rows across compounds with the
largest number of unique conformers. Values are scaled by descriptor row for
visualization.

```{r descriptor-heatmap, fig.height=7, fig.width=9}
top_heatmap_features <- feature_stats |>
  arrange(desc(SD)) |>
  slice_head(n = 36) |>
  mutate(Feature.Key = paste(Assay, Feature.ID, sep = ": "))

top_heatmap_compounds <- compound_metadata |>
  arrange(desc(GEOM.Unique.Conformers), GEOM.Source.SMILES) |>
  slice_head(n = 80) |>
  pull(GEOM.Source.SMILES)

heatmap_mat <- do.call(
  rbind,
  lapply(seq_len(nrow(top_heatmap_features)), \(index) {
    assay_name <- top_heatmap_features$Assay[[index]]
    feature_id <- top_heatmap_features$Feature.ID[[index]]
    values <- assay_mats[[assay_name]][
      feature_id,
      top_heatmap_compounds,
      drop = FALSE
    ]
    rownames(values) <- top_heatmap_features$Feature.Key[[index]]
    values
  })
)

heatmap_scaled <- t(scale(t(heatmap_mat)))
heatmap_scaled[!is.finite(heatmap_scaled)] <- 0

heatmap_tbl <- as.data.frame(heatmap_scaled) |>
  rownames_to_column("Feature.Key") |>
  as_tibble() |>
  pivot_longer(
    cols = -Feature.Key,
    names_to = "GEOM.Source.SMILES",
    values_to = "Scaled.Value"
  ) |>
  mutate(
    Feature.Key = factor(
      Feature.Key,
      levels = rev(top_heatmap_features$Feature.Key)
    ),
    GEOM.Source.SMILES = factor(
      GEOM.Source.SMILES,
      levels = top_heatmap_compounds
    )
  )

ggplot(
  heatmap_tbl,
  aes(x = GEOM.Source.SMILES, y = Feature.Key, fill = Scaled.Value)
) +
  geom_tile() +
  scale_fill_gradient2(
    low = "#3B6EA8",
    mid = "white",
    high = "#C75C5C",
    midpoint = 0
  ) +
  labs(
    title = "Scaled high-variance WHIM descriptor features",
    x = "Compounds ordered by unique conformer count",
    y = "Assay and feature",
    fill = "Scaled\nvalue"
  ) +
  theme(
    axis.text.x = element_blank(),
    axis.ticks.x = element_blank(),
    panel.grid = element_blank()
  )
```

## Basic Access Patterns

The MAE can be used directly as an analysis-ready compound descriptor resource.
Most analyses will either use one WHIM assay at a time or concatenate assay
families after confirming that the descriptor families are appropriate for the
question.

```{r access-one-compound}
example_compound <- compound_metadata |>
  filter(In.AnnotationDB) |>
  arrange(desc(GEOM.Unique.Conformers), GEOM.Source.SMILES) |>
  slice(1) |>
  pull(GEOM.Source.SMILES)

example_metadata <- compound_metadata |>
  filter(GEOM.Source.SMILES == example_compound) |>
  select(
    GEOM.Source.SMILES,
    Pubchem.CID,
    InChIKey,
    AnnotationDB.Name,
    GEOM.Total.Conformers,
    GEOM.Unique.Conformers,
    GEOM.Lowest.Energy,
    GEOM.Ensemble.Energy
  )

kable(example_metadata)
```

```{r access-one-descriptor-profile}
example_descriptors <- bind_rows(
  lapply(assay_names, \(assay_name) {
    tibble(
      Assay = assay_name,
      Feature.ID = rownames(assay_mats[[assay_name]]),
      value = assay_mats[[assay_name]][, example_compound]
    )
  })
) |>
  arrange(Assay, desc(abs(value))) |>
  group_by(Assay) |>
  slice_head(n = 3) |>
  ungroup()

kable(example_descriptors)
```

```{r access-pubchem-subset}
pubchem_subset <- compound_metadata |>
  filter(!is.na(Pubchem.CID)) |>
  slice_head(n = 100) |>
  pull(GEOM.Source.SMILES)

whim_hp_subset <- assay_mats[["WHIM_hp"]][, pubchem_subset, drop = FALSE]

tibble(
  subset = "First 100 PubChem-mapped GEOM compounds",
  compounds = ncol(whim_hp_subset),
  features = nrow(whim_hp_subset)
) |>
  kable()
```

```{r modeling-matrix}
tibble(
  object = c(
    "WHIM_hp feature_by_compound_matrix",
    "WHIM_hp compound_by_feature_matrix"
  ),
  rows = c(nrow(assay_mats[["WHIM_hp"]]), ncol(assay_mats[["WHIM_hp"]])),
  columns = c(ncol(assay_mats[["WHIM_hp"]]), nrow(assay_mats[["WHIM_hp"]]))
) |>
  mutate(
    rows = fmt_count(rows),
    columns = fmt_count(columns)
  ) |>
  kable()
```

The compound-by-feature orientation is typically the convenient format for
machine learning or clustering workflows, while the feature-by-compound
orientation matches the stored `SummarizedExperiment` assays.

## Session Info

```{r session-info}
sessionInfo()
```
